---
title: "Peer-graded Assignment: Course Project: Shiny Application and Reproducible Pitch"
author: "Irshad"
date: "4/30/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

**Overview**

This application was designed for Developing Data Products as part of the Coursera Data Science Speicalization Course.

The first part of the assignment to create a Shiny application can be found here: https://agmgaffar.shinyapps.io/shinyappirshad/

The second part of the assigment to prepare a reproducible pitch presentation about the application can be found here: https://github.com/agmgaffar123/Shinyapp.github.io

This model is developed based on mtcars data set.The model will predict the hoursepower based on milage and bins.



## Data abd Variables given

- Input - Milage
- Output - Horsepower
- Data - Mtcars

## Slide with R Output

```{r cars, echo = TRUE,comment = ""}
head(mtcars)
```

## Slide with Plot

Model - model_lm <- lm(hp~mpg, data = mtcars)

Summary

```{r, comment = "", echo = TRUE, fig.align='center'}
model_lm <- lm(hp~mpg, data = mtcars)
summary(model_lm)
```

